Workflow

### 2014-07-25 Workflow/Workflow.Rmd
Improved Workflow.Rmd file. Added bulleted lists.

### Add new data
Add the file named `<Source>.txt` in the data directory.   
Edit the `Packages/EconData/R/Constants.R` file to include `<Source>` in the `dataSource` variable.   
Add any Excel workbooks or other metadata in `data/Excel Workbooks/<Source>`.

### Create historical data frame
Run `Scripts/PreProcess.R -S <Source>` to create the historical data frame for `<Source>`.    
The file will be stored at `Packages/EconData/data/<Source>.rda`.    
This command can be run on a laptop, because it is fast.    
Build and reload the EconData package.    
Push the changes to GitHub.   
On acc, Pull from GitHub.     
On dahl (node-00), say `install_github("MatthewHeun/Econ-Growth-R-Analysis/Packages/EconData")`.

### Create the batch script
Create the file `Scripts/<Source>_batch.bash` file.     
It is probably best to modify an existing `<Source>_batch.bash file.`      
Be sure to edit the `OUTDIR` variable to be `OUTDIR="$LOC_PATH/data_resample/<Source>"`     
Change the final line (the one that runs the `OrigModels.R script`) to be
`ssh node-xx "cd $LOC_PATH; Scripts/OrigModels.R -S <Source> &> $OUTDIR/node-xx.txt" &`        
Distribute the work over the nodes in a way that makes sense.
Push the file to GitHub.      
On dahl, pull from GitHub.

### Submit the job to dahl
Run `Scripts/<Source>_batch.bash` on dahl.

### Post-process the results
Run `PostProcess.R -R data_resample/<Source>` on dahl to create
`Packages/EconData/data/<Source>_Coeffs.rda` and
`Packages/EconData/data/<Source>_Fitted.rda`.
Note that this command will need to be issued from a node of the cluster, not from `fs1.calvin.edu`.

### Add to EconData package
From acc, push the changes to GitHub to make the new files available.
Pull from GitHub on a local laptop, and rebuild the `EconData` package.
At this point, all new results should be available in the `EconData` package.

>>>>

### Add new data
* Add the file named `<Source>.txt` in the data directory.   
* Edit the `Packages/EconData/R/Constants.R` file to include `<Source>` in the `dataSource` variable.   
* Add any Excel workbooks or other metadata in `data/Excel Workbooks/<Source>`.

### Create historical data frame
* Run `Scripts/PreProcess.R -S <Source>` to create the historical data frame for `<Source>`.
The file will be stored at `Packages/EconData/data/<Source>.rda`.
This command can be run on a laptop, because it is fast.    
* Build and reload the EconData package.    
* Push the changes to GitHub.   
* On acc, Pull from GitHub.     
* On dahl (node-00), say `install_github("MatthewHeun/Econ-Growth-R-Analysis/Packages/EconData")`.

### Create the batch script
* Create the file `Scripts/<Source>_batch.bash` file.
  + It is probably best to modify an existing `<Source>_batch.bash file.`      
  + Be sure to edit the `OUTDIR` variable to be `OUTDIR="$LOC_PATH/data_resample/<Source>"`     
  + Change the final line (the one that runs the `OrigModels.R script`) to be
`ssh node-xx "cd $LOC_PATH; Scripts/OrigModels.R -S <Source> &> $OUTDIR/node-xx.txt" &`        
  + Distribute the work over the nodes in a way that makes sense.
* Push the file to GitHub.      
* On dahl, pull from GitHub.

### Submit the job to dahl
* Start with `Scripts/<Source>_batch.bash "-n 2 -C"`.
* Then do `Scripts/<Source>_batch.bash "-n 1000 -C"`.

### Post-process the results
* Run `PostProcess.R -R data_resample/<Source>` on dahl to create
`Packages/EconData/data/<Source>_Coeffs.rda` and
`Packages/EconData/data/<Source>_Fitted.rda`.
Note that this command will need to be issued from a node of the cluster (e.g., node-00), not from `fs1.calvin.edu`.

### Add to EconData package
* From acc, push the changes to GitHub to make the new files available.
* Pull from GitHub on a local laptop, and rebuild the `EconData` package.

At this point, all new results should be available in the `EconData` package.
